Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies along a climatic gradient in the rear-edge

### 2019-06-24 man/ecosystems/ms_ecosystems.Rmd
update

Drought events produced reduction of RWI for all sites (Figure S3), being particularly evident the negative effect of the 1995 drought, when the greatest reduction of tree-growth were recorded for all chronologies. Southern sites (CA-High and CA-Low) showed weaker reductions than the northern site (SJ), especially for 2005 and 2012 (Figure S3). Trees from northern site also suffered a great reduction during 1945-1946 drought event (Figure 5).

`$TODO$ PASAR A Discussion` The analysis of growth changes revealed differences in forest history between sites (Figures 5 and S4).

>>>>

Drought events produced reduction of RWI for all sites (Figure S3), being particularly evident the negative effect of the 1995 drought, when the greatest reduction of tree-growth were recorded for all chronologies. The southern sites (CA-High and CA-Low) showed weaker reductions of tree-growth than the northern site (SJ), especially for 2005 and 2012 (Figure S3). Tree-growth reduction followed a moisture-gradient, being weaker for the wetter site (CA-High). Trees from northern site also suffered a great reduction during 1945-1946 drought event (Figure 5).
